A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-03-26 controlled_study.tex
use lstinline

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}
  % \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{tikz,pgfplots,pgfplotstable}
  \usepackage{mathtools}
  \usepgfplotslibrary{statistics}
\else
\fi

@@

\begin{itemize}
  \item \textbf{R1. Representative API.} We had to choose an existing REST API that is currently used by API client developers. Selecting a mature REST API for this study reduces the possibility that the obstacles we observe in the study are the results of insignificant accidental problems symptomatic of an immature technology. A familiar domain needed to be selected so that participants are able to relate to the API features without requiring upfront training. In addition to selecting the API, we had to select tasks that are related to the core features provided by the API to represent reality.
  \item \textbf{R2. Open source.} To be able to understand the impact of usage examples, we needed to select an open-source API where we can add new examples to the documentation for performing this study.
  \item \textbf{R3. Time bound.} The total time spent by each participant is required to be time bound to measure the rate of success within a limited time frame. As a result, the study needs to be setup such that participants are able to focus on performing the tasks minimizing any overhead.
  \item \textbf{R4. Participant Selection.} Developers with prior experience on REST APIs need to be recruited as study participants to perform the study within a limited amount of time and in a realistic setup. Furthermore, to reduce a learning bias, only participants with no prior experince of using the WordPress REST API V2 are accepted for this study.
\end{itemize}

@@

Starting January 2017, the WordPress REST API V2 is no longer required to be installed as a separate plug-in since it is bundled with WordPress installation. According to the code repository, there are a total of 99 and 46 contributors that had at least one commit to the code repository of the API and its documentation, respectively. These properties satisfy R1, our requirements for using a representative API. By selecting an open-source project we are able to access the source-code to inspect the implementation and documentation technique of the WordPress REST API. The API implements a self-documenting feature where API developers expose API endpoints over HTTP OPTIONS verb to explain the API elements. To implement this feature, the API developers describe the API elements in the code. For example:

\lstset{basicstyle=\footnotesize}
\begin{lstlisting}[language=php,breaklines=true,showspaces=false,showstringspaces=false,numbers=left,xleftmargin=2em,caption={Example of self-documenting API Code in PHP},label=wordpress_code]
public function get_item_schema() {
  $schema = array(
    '$schema'    => 'http://json-schema.org/draft-04/schema#',
    'title'      => $this->post_type,
    'type'       => 'object',
    /*
     * Base properties for every Post.
     */
    'properties' => array(
        'date'            => array(
            'description' => __( "The date the object was published, in the site's timezone." ),
            'type'        => 'string',
            'format'      => 'date-time',
            'context'     => array( 'view', 'edit', 'embed' ),
        ),...
\end{lstlisting}

On Listing \ref{wordpress_code}, line 4 specifies that this is a schema definition for the API element $Post$. On Line 10, it defines $date$, one of the properties of $Post$, followed by a human readable description and type information. On line 14, the context of this property is mentioned as $view, edit, embed$, meaning that this property will be returned when the $Post$ object is returned, embedded, or can be used as an input for editing.

The WordPress team leverages this self-documenting feature to generate and publish the official API documentation as an HTML website. Fig. \ref{fig:schema} shows a screenshot of the published documentation for the $date$ attribute of the $Post$ API element.\footnote{\url{http://v2.wp-api.org/reference/posts/}}

@@

The participants are requested to perform a total of six tasks using the API including one practice task. All of the tasks are related to a single API element, $Post$\footnote{A Post identifies a blog post within WordPress}. The tasks get progressively more difficult, and all but the last task can be performed independently of each other. Participants are requested to limit the total time on the study to a maximum of one hour. Participants are encouraged to proceed to the next task when they are either satisfied with their answer or feel stuck and unable to make progress.

@@

To verify the response of an API call, the API client developers can use HTTP response headers and/or HTTP response body. To perform the tasks, the participants are required to use one or more of the inputs I1-4. In the following paragraphs, we describe each task with its description and the study observation goals against the aforementioned API input and output information. For each of the tasks, the participants are required to use the same WordPress REST API and accompanying documentation.

@@

\textbf{T2: Filter posts by author task.} The participants are asked to use the API to filter the list of posts obtained in T1 by an author given the author's user name. To answer this correctly, the participants are required to first make an API call to get the numeric ID of the author given the string based user name. Then, the ID needs to be used on the Post API to filter posts by the author. This task allows us to understand the impact of usage examples on API client developers when multiple API calls need to be made to perform a task using the API. Inputs I1-2 are required to complete this task successfully.

@@

\textbf{T6: Update post task.} We ask the participants to use the API to update a blog post that they published in T5 with a new excerpt. Similar to T5, this task requires the use of inputs I1-4, but with different values for the inputs. This task allows us to understand API client developer productivity on inter-dependent tasks with respect to usage examples.

@@

To satisfy the requirement of developers with REST API experience (R3), we used the following criteria for recruiting the study participants:

@@

We conducted two pilot studies to evaluate and understand an effective process for performing this study. The first pilot study involved four participants that were invited to join the first author in-person or over video conferencing. The study involved tasks using two APIs, the WordPress REST API V2 and the GMail REST API. Each participant was given one of the two APIs and the tasks T1-T6 and online answer forms to complete using the API within an hour. The primary findings from this pilot are as follows: 1) participants required significant overhead time to setup a development environment with the proper API credentials, 2) the intermediate trial attempts of using the API are potentially more valuable than the final answer as it allows us to study what obstacles the participants face, 3) the number of tasks for the study had to be reduced to fit within the one hour limit, and 4) for the GMail API, participants used up a large portion of their time on learning about how to use  OAuth.

@@

\subsubsection{Protocol}
\label{sub:protocol}
Learning from the pilot studies, we designed the main study protocol as follows: we enhanced the original WordPress REST API documentation and added a total of 3 API usage examples to show listing of blog posts with query parameters for filtering, a request to create a blog post and a request to update a blog post. We used the WordPress API unit tests to find relevant data for these examples. Fig. \ref{fig:original} shows a screenshot of the original API documentation related to T4 where the API client developers are provided with a reference table describing the different properties that can be used to create a $Post$ object\footnote{\url{http://v2.wp-api.org/reference/posts/}}. Fig. \ref{fig:enhanced} shows a screenshot of the enhanced API documentation with a cURL based usage example. cURL is used because it is used by elsewhere in the original API documentation. In the enhanced API documentation, the example shows one possible API call with realistic values for the data that is described in the reference table and associated API response headers and body.

We divided the participants into two groups, G1 and G2. G1 participants were provided with a link to the official API documentation on the web-based API explorer, and G2 participants were provided with a link to the enhanced API documentation with usage examples. The web-based API explorer allocated more participants to G1 compared to G2 because we wanted to better understand the impact of the lack of usage examples on API client developer productivity. However, each individual participant was randomly assigned to a group by the web-based API explorer. All participants were given the same set of API tasks and were requested to limit their participation time to a maximum of one hour. No task specific time limit was imposed except an overall limit one hour for the entire study because we wanted participants to spend sufficient time on each task without forcing them to move to the next one. Participants were allowed to access the internet and external resources alongside the provided API documentation to perform the tasks as they would normally use on a typical work day. We used the web-based API explorer to also collect an experience rating on a scale of 0-10, 10 being the best possible, of using the given REST API documentation and a free-form feedback from each participant as an exit survey.

@@

\textbf{Success Rate} = (total number of successful tasks by group) / (number of participants in group * number of API tasks)

\textbf{Average Trial API Calls} = (number of API calls annotated as successful) / (total number of trial API calls made by group)

\textbf{Average Time Spent} = (number of successful API tasks by group) / (total time spent by all participants in the group)

@@

Even though we expected G2 to outperform G1, we were surprised to see the difference in effort vs. success of the two groups. In Fig. \ref{graph:productivity} and \ref{graph:time} we see that, for the simpler tasks, T2 and T3, G1 required more time and more trial API calls and reached successful answers with a lower percentage compared to G2. For T4, where the participants are required to inspect an HTTP response header, G2 needed more API calls on average, but also yielded 24\% higher success rate. For the more complex tasks T5 and T6, we see that participants in G1 had very low success rate and very high number of average API trials compared to G2. The data here depicts that without usage examples developers spend more time and require more trial and error attempts yet resulting in lower success rates, and the situation gets worse for relatively complicated tasks.

@@

11 of the 16 G1 participants mentioned the lack of examples with HTTP headers, request and response as the primary problem with the API documentation. On the other hand, 7 out of the 10 G2 participants mentioned the examples being helpful from the enhanced documentation. Based on these feedback, we identify usage examples as the most frequent and central topic of interest from our participants. This is also supported by our quantitative analysis results as discussed earlier in this section. REST API developers need to provide usage examples showing sample requests and responses with HTTP headers and body for API actions to help API usability. In the remainder of this section, we provide our observations related to each task and their implications.

\textbf{Observation: Use of Data Type.} Without usage examples, we observed 10 of the 16 G1 participants used incorrect data type of $String$ instead of $Integer$. To successfully complete T1, participants had to use an integer ID representing an $Author$ object given the author name. In the original API documentation, the following is mentioned about the author parameter: ``author: Limit result set to posts assigned to specific authors.'' The documentation doesn't mention that the data type required is the numeric author ID, not the author name. P1.12 mentioned the following: \textit{``...to find posts for the author, I had to inspect the response to see that indeed the $author\_id$ was in there''}. The enhanced documentation showed one example of using numeric ID. 3 of the 10 participants from G2 ran into the same error. When faced with this error, participants used trial and error to eventually complete the task.

@@

\textbf{Observation: Use of Data Format.} We observed participants in G1 faced obstacles using correct data formats for Date and Array type data in API requests without usage examples. Tasks T3 required the use of a correct format to represent an array of numeric post IDs to be excluded using the API. The original documentation mentions the following about this API query parameter: ``exclude: Ensure result set excludes specific IDs.'' Participants attempted to solve this task using multiple different formats for specifying the array. For example: they tried with $exclude=[1,4]$, $exclude=1\&4$, $exclude=4\&\&exclude=1$, $id!=1\&id!=4$ and other alternatives before eventually finding the right format as follows $exclude=1,4$. Participant P1.6 mentioned the following: \textit{``It was difficult to figure out whether some of the inputs needed to be arrays or just a comma-separated list.''}. 7 out of the 16 participants in G1 faced this error. The enhanced documentation showed one example of using multiple IDs and all G2 participants could use the right format.

Task T5 also required the participants to use an ISO8601 formatted date for publishing a post with a specific date. Even though the original documentation mentions ISO8601 format, it doesn't provide an example. Instead of using ``2016-01-01T00:00:00-00:00'', participants from G1 used date formats as follows: ``January 1, 2016'', ``2016-01-01T12:00:00'', ``20160101'', etc. P1.8 mentioned the following: \textit{``Got hung up trying to figure out the formatting of the date (which doesn't appear to be ISO8601, despite what it says)''}. After analyzing the response, we found that P1.8 used the ISO8601 formatted date in the API calls, but didn't provide the $second$ portion of the time as required by the API. 8 of the 16 participants in G1 had an error in the date formats. With an example, 1 of the 10 participants had the same error from G2.

@@

\textbf{Observation: Use of Request Headers.} We were surprised to see that 14 of the 15 G1 participants that tried T5 and T6 faced problem using correct request headers without usage examples. Tasks T5 and T6 required the use of a HTTP request header named $Content-Type$. In the original API documentation, the following was mentioned: ``The API uses JSON exclusively as the request and response format, including error responses.''. Experienced software engineers still had problem using this HTTP header as we found from the participants in G1. P1.12 mentioned the following: \textit{``I didn't know how to specify application/json so that I could send POST data via the body instead in the URL parameters... Examples would really help - with a sample request and a sample response.''}  Even though G1 participants have years of experience with REST APIs, only one of them could use the $Content-Type$ header correctly without example. In contrast, 2 out of the 10 participants from G2 failed to use this header correctly as indicated in the example in the enhanced documentation. Moreover, 1 of the 2 G2 participants that didn't use the header first time, later used it correctly on a subsequent attempt.

@@

\textbf{Observation: Use of Interdependent API Calls.} We observed the G1 participants had problem completing API tasks that require multiple API calls without usage examples. Tasks T2 and T6 required the use of multiple API calls to complete successfully. Both tasks require an initial API call to find data using the API that is needed make a second API call. For example, P1.5 mentioned the following about T6, \textit{``The post I created is not visible and not editable, though I got 201. Not sure why''}. After analyzing the response, we observed that P1.5 was able to create a blog post, but failed to publish it because it didn't have the $publish$ status. As a result, the post was not returned via the API for T6. P2.2 mentioned the following about T2: \textit{``In case of search posts by author, it's not clear how to find the author\_id. Although, I realized that users and authors are same in this case.''}

>>>>

\ifCLASSINFOpdf
  \usepackage{listings}
  \usepackage[pdftex]{graphicx}
  \usepackage{url}
  % \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{tikz,pgfplots,pgfplotstable}
  \usepackage{mathtools}
  \usepgfplotslibrary{statistics}
  \usepackage{courier}
\else
\fi

@@

\begin{itemize}
  \item \textbf{R1. Representative API.} We had to choose an existing REST API that is currently used by API client developers. Selecting a mature REST API for this study reduces the possibility that the obstacles we observe in the study are the results of insignificant accidental problems symptomatic of an immature technology. We selected a familiar domain so that participants are able to relate to the API features without requiring upfront training. In addition to selecting the API, we had to select tasks that are related to the core features provided by the API to represent a common usage area of the API.
  \item \textbf{R2. Open source.} To be able to understand the impact of usage examples, we needed to select an open-source API where we can add new examples to the documentation for performing this study.
  \item \textbf{R3. Time bound.} We applied a maximum time constraint for each participant to measure the rate of success within a limited time frame. As a result, the study needs to be setup such that participants are able to focus on performing the tasks minimizing any overhead.
  \item \textbf{R4. Participant Selection.} Developers with prior experience on REST APIs need to be recruited as study participants to perform the study within a limited amount of time and in a realistic setup. Furthermore, to reduce a learning bias, only participants with no prior experince of using the WordPress REST API V2 are accepted for this study.
\end{itemize}

@@

Starting January 2017, the WordPress REST API V2 is no longer required to be installed as a separate plug-in since it is bundled with WordPress installation. According to the code repository, there are a total of 99 and 46 contributors that had at least one commit to the code repository of the API and its documentation, respectively. These properties satisfy R1 AND R2, our requirements for using a representative API. By selecting an open-source project we are able to access the source-code to inspect the implementation and documentation technique of the WordPress REST API. The API implements a self-documenting feature where API developers expose API endpoints over HTTP OPTIONS verb to explain the API elements. To implement this feature, the API developers describe the API elements in the code. For example:

\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}
\begin{lstlisting}[language=php,showspaces=false,showstringspaces=false,numbers=left,xleftmargin=2em,caption={Example of self-documenting API Code in PHP},label=wordpress_code]
public function get_item_schema() {
  $schema = array(
    '$schema'    => 'http://json-schema.org/draft-04/schema#',
    'title'      => $this->post_type,
    'type'       => 'object',
    /*
     * Base properties for every Post.
     */
    'properties' => array(
        'date'            => array(
            'description' => __( "The date the object was published, in the site's timezone." ),
            'type'        => 'string',
            'format'      => 'date-time',
            'context'     => array( 'view', 'edit', 'embed' ),
        ),...
\end{lstlisting}

On Listing \ref{wordpress_code}, line 4 specifies that this is a schema definition for the API element \lstinline{Post} \footnote{\url{https://github.com/WP-API/WP-API}}. On Line 10, it defines \lstinline{date}, one of the properties of \lstinline{Post}, followed by a human readable description and type information. On line 14, the context of this property is mentioned as \lstinline{view, edit, embed}, meaning that this property will be returned when the \lstinline{Post} object is returned, embedded, or can be used as an input for editing.

The WordPress team leverages this self-documenting feature to generate and publish the official API documentation as an HTML website. Fig. \ref{fig:schema} shows a screenshot of the published documentation for the \lstinline{date} attribute of the \lstinline{Post} API element.\footnote{\url{http://v2.wp-api.org/reference/posts/}}

@@

The participants are requested to perform a total of six tasks using the API including one practice task. All of the tasks are related to a single API element, \lstinline{Post}\footnote{A Post identifies a blog post within WordPress}. The tasks get progressively more difficult, and all but the last task can be performed independently of each other. Participants are requested to limit the total time on the study to a maximum of one hour (R3). Participants are encouraged to proceed to the next task when they are either satisfied with their answer or feel stuck and unable to make progress.

@@

To verify the response of an API call, the API client developers can use HTTP response headers and/or HTTP response body. To perform the tasks, the participants are required to use one or more of the inputs I1-4. In the following paragraphs, we describe each task with its description and the study observation goals against the aforementioned API input and output information. For each of the tasks, the participants are required to the same WordPress REST API and one of the two variants of accompanying documentation.

@@

\textbf{T2: Filter posts by author task.} The participants are asked to use the API to filter the list of posts obtained in T1 by an author given the author's user name. To answer this correctly, the participants are required to first make an API call to get the numeric ID of the author given the string based user name. Then, the ID needs to be used on the \lstinline{Post} API to filter posts by the author. This task allows us to understand the impact of usage examples on API client developers when multiple API calls need to be made to perform a task using the API. Inputs I1-2 are required to complete this task successfully.

@@

\textbf{T6: Update post task.} We ask the participants to use the API to update a blog \lstinline{Post} that they published in T5 with a new \lstinline{excerpt}. Similar to T5, this task requires the use of inputs I1-4, but with different values for the inputs. This task allows us to understand API client developer productivity on inter-dependent tasks with respect to usage examples.

@@

To satisfy the requirement of developers with REST API experience (R4), we used the following criteria for recruiting the study participants:

@@

We conducted two pilot studies to evaluate and understand an effective process for performing this study. The first pilot study involved four participants that were invited to join the first author in-person or over video conferencing. The study involved tasks using two APIs, the WordPress REST API V2 and the GMail REST API. Each participant was given one of the two APIs and and a set of API tasks and online answer forms to complete using the API within an hour. The primary findings from this pilot are as follows: 1) participants required significant overhead time to setup a development environment with the proper API credentials, 2) the intermediate trial attempts of using the API are potentially more valuable than the final answer as it allows us to study what obstacles the participants face, 3) the number of tasks for the study had to be reduced to fit within the one hour limit, and 4) for the GMail API, participants used up a large portion of their time on learning about how to use  OAuth.

@@

\subsubsection{Protocol}
\label{sub:protocol}
Learning from the pilot studies, we designed the main study protocol as follows: we enhanced the original WordPress REST API documentation and added a total of 3 API usage examples to show listing of blog posts with query parameters for filtering, a request to create a blog post and a request to update a blog post. We used the WordPress API unit tests to find relevant data for these examples. Fig. \ref{fig:original} shows a screenshot of the original API documentation related to T4 where the API client developers are provided with a reference table describing the different properties that can be used to create a \lstinline{Post} object\footnote{\url{http://v2.wp-api.org/reference/posts/}}. Fig. \ref{fig:enhanced} shows a screenshot of the enhanced API documentation with a cURL\footnote{\url{https://curl.haxx.se/}} based usage example. cURL is used because it is used elsewhere in the original API documentation. In the enhanced API documentation, the example shows one possible API call with realistic values for the data that is described in the reference table and associated API response headers and body.

We divided the participants into two groups, G1 and G2. G1 participants were provided with a link to the official API documentation on the web-based API explorer, and G2 participants were provided with a link to the enhanced API documentation with usage examples. We designed the the web-based API explorer to allocate more participants to G1 compared to G2 because we wanted to better understand the impact of the lack of usage examples on API client developer productivity. However, each individual participant was randomly assigned to a group by the web-based API explorer. All participants were given the same set of API tasks and were requested to limit their participation time to a maximum of one hour. No task specific time limit was imposed except an overall limit of one hour for the entire study because we wanted participants to spend sufficient time on each task without forcing them to move to the next one. Participants were allowed to access the internet and external resources alongside the provided API documentation to perform the tasks as they would normally use on a typical work day. We used the web-based API explorer to also collect an experience rating on a scale of 0-10, 10 being the best possible, of using the given REST API documentation and a free-form feedback from each participant as an exit survey.

@@

\textbf{Success Rate (Task, Group)} = (No. of participants that successfully completed Task) / (No. of participants in Group)

\textbf{Average Trial API Calls (Task, Group)} = (No. of API calls made by Group on Task) / (No. of participants in Group).

\textbf{Average Time Spent (Task, Group)} = (Time spent by Group on Task) / (No. of participants in Group)

@@

Even though it is expected that G2 would outperform G1 with an enhanced documentation, we were surprised to see the difference in effort vs. success of the two groups. In Fig. \ref{graph:productivity} and \ref{graph:time} we see that, for the simpler tasks, T2 and T3, G1 required more time and more trial API calls and reached successful answers with a lower percentage compared to G2. For T4, where the participants are required to inspect an HTTP response header, G2 needed more API calls on average, but also yielded 24\% higher success rate. For the more complex tasks T5 and T6, we see that participants in G1 had very low success rate and very high number of average API trials compared to G2. The data here depicts that without usage examples developers spend more time and require more trial and error attempts yet resulting in lower success rates, and the situation gets worse for relatively complicated tasks.

@@

11 of the 16 G1 participants mentioned the lack of examples with HTTP headers, request and response as the primary problem with the API documentation. On the other hand, 7 out of the 10 G2 participants mentioned the examples being helpful from the enhanced documentation. We identify usage examples as the most frequent and central topic of interest from our participants as per their feedback. This is also supported by our quantitative analysis results as discussed earlier in this section. REST API developers need to provide usage examples showing sample requests and responses with HTTP headers and body for API actions to help API usability. In the remainder of this section, we provide our observations related to each task and their implications.

\textbf{Observation: Use of Data Type.} Without usage examples, we observed 10 of the 16 G1 participants used incorrect data type of \lstinline{String} instead of \lstinline{Integer}. To successfully complete T1, participants had to use an integer ID representing an \lstinline{Author} object given the author name. In the original API documentation, the following is mentioned about the author parameter: ``author: Limit result set to posts assigned to specific authors.'' The documentation doesn't mention that the data type required is the numeric author ID, not the author name. P1.12 mentioned the following: \textit{``...to find posts for the author, I had to inspect the response to see that indeed the $author\_id$ was in there''}. The enhanced documentation showed one example of using numeric ID. 3 of the 10 participants from G2 ran into the same error. When faced with this error, participants used trial and error to eventually complete the task.

@@

\textbf{Observation: Use of Data Format.} We observed participants in G1 faced obstacles using correct data formats for Date and Array type data in API requests without usage examples. Tasks T3 required the use of a correct format to represent an array of numeric post IDs to be excluded using the API. The original documentation mentions the following about this API query parameter: ``exclude: Ensure result set excludes specific IDs.'' Participants attempted to solve this task using multiple different formats for specifying the array. For example: they tried with \lstinline{exclude=[1,4], exclude=1&4, exclude=4&&exclude=1, id!=1&id!=4} and other alternatives before eventually finding the right format as follows \lstinline{exclude=1,4}. Participant P1.6 mentioned the following: \textit{``It was difficult to figure out whether some of the inputs needed to be arrays or just a comma-separated list.''}. 7 out of the 16 participants in G1 faced this error. The enhanced documentation showed one example of using multiple IDs and all G2 participants could use the right format.

Task T5 also required the participants to use an ISO8601 formatted date for publishing a post with a specific date. Even though the original documentation mentions ISO8601 format, it doesn't provide an example. Instead of using ``2016-01-01T00:00:00-00:00'', participants from G1 used date formats as follows: \lstinline{``January 1, 2016'', ``2016-01-01T12:00:00'', ``20160101''}. P1.8 mentioned the following: \textit{``Got hung up trying to figure out the formatting of the date (which doesn't appear to be ISO8601, despite what it says)''}. After analyzing the response, we found that P1.8 used the ISO8601 formatted date in the API calls, but didn't provide the required \lstinline{second} portion of the time. 8 of the 16 participants in G1 had an error in the date formats. With an example, 1 of the 10 participants had the same error from G2.

@@

\textbf{Observation: Use of Request Headers.} We were surprised to see that 14 of the 15 G1 participants that tried T5 and T6 faced problem using correct request headers without usage examples. Tasks T5 and T6 required the use of a HTTP request header named \lstinline{Content-Type}. In the original API documentation, the following was mentioned: ``The API uses JSON exclusively as the request and response format, including error responses.''. Experienced software engineers still had problem using this HTTP header as we found from the participants in G1. P1.12 mentioned the following: \textit{``I didn't know how to specify application/json so that I could send POST data via the body instead in the URL parameters... Examples would really help - with a sample request and a sample response.''}  Even though G1 participants have years of experience with REST APIs, only one of them could use the \lstinline{Content-Type} header correctly without example. In contrast, 2 out of the 10 participants from G2 failed to use this header correctly as indicated in the example in the enhanced documentation. Moreover, 1 of the 2 G2 participants that didn't use the header first time, later used it correctly on a subsequent attempt.

@@

\textbf{Observation: Use of Interdependent API Calls.} We observed the G1 participants had problem completing API tasks that require multiple API calls without usage examples. Tasks T2 and T6 required the use of multiple API calls to complete successfully. Both tasks require an initial API call to find data using the API that is needed make a second API call. For example, P1.5 mentioned the following about T6, \textit{``The post I created is not visible and not editable, though I got 201. Not sure why''}. After analyzing the response, we observed that P1.5 was able to create a blog post, but failed to publish it because it didn't have the \lstinline{publish} status. As a result, the post was not returned via the API for T6. P2.2 mentioned the following about T2: \textit{``In case of search posts by author, it's not clear how to find the author\_id. Although, I realized that users and authors are same in this case.''}
